Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2015-11-17 ijar-npb-ms.tex
par on near-noninformative prior sets, sets of R_sys in separate section

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}

@@

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{{\bm#1}}

@@

\section{Reparametrisation of the Beta}

@@

The Beta-binomial distribution in terms of the updated parameters $\nn$ and $\yn$,
now again with indicators $t$ and $k$,
is therefore
\begin{align*}
P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
                                                    {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \,.
\end{align*}
\td{leave this equation out???}

@@

***Illustration of such prior-data conflict with $\bebin$ distribution:
different priors updated to same posterior,
or same prior updated to different posteriors with same variance,
show corresponding $C^k_t$ distribution.***

\section{Sets of Priors}

As was shown in \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
we can have both tractability and meaningful reaction to prior-data conflict
by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
(A detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
corresponds to a Beta prior, thus $\MktZ$ is a set of Beta priors.
The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
obtained from updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
and so can be described efficiently through the set of updated parameters
\begin{align*}
\PktN &= \Big\{ (\nktn, \yktn) \mid (\nktz, \yktz) \in \PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu] \Big\}\,.
\end{align*}
Such rectangular prior parameter sets $\PktZ$ have been shown
to balance desirable model properties and ease of elicitation quite well.

For each component type $k$ and time point $t$,
one has to choose only the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
(so $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions characterizing
prior knowledge on the survival function of components of type $k$);
notwithstanding this, the model has favourable inference properties.

@@

@@

***e.g., what to do in extreme tail of component distributions?
How sensitive is the method to choosing prior (lower, upper) mean zero for $p^k_t$ at high $t$'s?***

@@

***Vacuous prior sets: $[\yktzl, \yktzu] = [0,1]$ combined with both fixed $\nktz$ and interval $[\nktzl, \nktzu]$)?***

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}

@@

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\renewcommand{\vec}[1]{{\bs#1}}

@@

\section{Reparametrisation of the Beta Distribution}

@@

The Beta-binomial distribution in terms of the updated parameters $\nn$ and $\yn$,
now again with indicators $t$ and $k$,
is therefore
\begin{align}
P(C^k_t = l_k \mid s^k_t) &= {m_k \choose l_k} \frac{B(l_k + \nn_{k,t}\yn_{k,t}, m_k - l_k + \nn_{k,t}(1-\yn_{k,t}))}
                                                    {B(\nn_{k,t}\yn_{k,t}, \nn_{k,t}(1-\yn_{k,t}))} \,.
\label{eq:postpredCny}
\end{align}
\td{leave this equation out???}

@@

\td{***Illustration of such prior-data conflict with $\bebin$ distribution:
different priors updated to same posterior,
or same prior updated to different posteriors with same variance,
show corresponding $C^k_t$ distribution.***}

\section{Sets of Beta Priors}

As was shown in \citet{2009:WalterAugustin}, %Walter \& Augustin (2009),
we can have both tractability and meaningful reaction to prior-data conflict
by using sets of priors $\MktZ$ produced by parameter sets $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
(A detailed discussion of different choices for $\PktZ$ is given in \citet[\S 3.1]{2013:diss-gw}.)
In our model, each prior parameter pair $(\nktz, \yktz) \in \PktZ$
corresponds to a Beta prior, thus $\MktZ$ is a set of Beta priors.
The set of posteriors $\MktN$ is obtained by updating each prior in $\MktZ$ according to Bayes' Rule.
Due to conjugacy, $\MktN$ is a set of Beta distributions with parameters $(\nktn, \yktn)$
obtained from updating $(\nktz, \yktz) \in \PktZ$ according to \eqref{eq:nyupdate},
and so can be described efficiently through the set of updated parameters
\begin{align*}
\PktN &= \Big\{ (\nktn, \yktn) \mid (\nktz, \yktz) \in \PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu] \Big\}\,.
\end{align*}
Such rectangular prior parameter sets $\PktZ$ have been shown
to balance desirable model properties and ease of elicitation quite well.
%
For each component type $k$ and time point $t$,
one has to choose only the four parameters $\nktzl, \nktzu, \yktzl, \yktzu$
(so $4 \times |{\cal T}|$ parameters are needed to define the set of prior distributions characterizing
prior knowledge on the survival function of components of type $k$);
notwithstanding this, the model has favourable inference properties.

@@

Furthermore, with sets of Beta priors it is also possible
to express prior ignorance in a more adequate way,
by letting $\yktzl \to 0$ and $\yktzu \to 1$
for some or all $t \in {\cal T}$.
(It is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$,
as this can lead to improper posterior predictive distributions.
E.g., for any $t < \min(\vec{t}^k)$,
we would get $\yktnu = 1$, leading to one argument of the Beta function
in the denominator of \eqref{eq:postpredCny} being zero.)
Choosing these limits for $\yktz$ means that we are prepared to give trivial bounds for the functioning probability only,
and do not wish to make any commitments about $p^k_t$ a priori.
Compare this to the uniform prior over $[0,1]$, a usual choice of `noninformative' prior,
being a Beta prior with $\alpha^k_t = \beta^k_t = 1$, i.e., $\nktz = 2$, $\yktz = 0.5$.
Taking this for all $t \in {\cal T}$ means that we expect the component reliability function
to be on average 1/2 for all $t$, a very peculiar assumption,
and, in our view, quite incompatible with the notion of prior ignorance.

In this near-noninformative setting, the choice of $\nktzl$ not relevant,
as both $\yktnl$ and $\yktnu$ are obtained with $\nktzu$;
indeed $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
$\frac{s^k_t}{n_k} \in [\yktzl, \yktzu]$ for all $t \in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
Logically, one cannot have prior-data conflict in case of prior near ignorance.

\td{***called near-noninformative, for near-noninformative sets when $\yz$ is not bounded see
benavoli zaffalon papers***}

\section{Sets of System Reliability Functions}

@@

***e.g., what to do in extreme tail of component distributions?
How sensitive is the method to choosing prior (lower, upper) mean near-zero for $p^k_t$ at high $t$'s?***

***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
to get proper posteriors!?!***

@@

***Vacuous prior sets: $[\yktzl, \yktzu] = (0,1)$ combined with interval $[\nktzl, \nktzu]$)***
